**The statistical analysis of non-linear longitudinal data in biomedical research using generalized additive models**

### 2021-05-23 Manuscripts/Manuscript by chapters -v1/Full_document.Rmd
Aesthetics, need to add pairwise comparison code to the Appendix

library(patchwork)
library(tidyverse)
library(mvnfast)
library(nlme)
library(ggsci)
library(mgcv)
library(gratia)
library(ghibli)
set.seed(1) #set seed for reproducibility

@@

thm<-scale_color_ghibli_d("PonyoMedium",direction=1) #global theme for plotting
thm1<-scale_fill_ghibli_d("PonyoMedium",direction=1) #global theme for plotting

#this function will remove the default "author information" that is the Pandoc Latex template. Otherwise, and additional "and" will appear at the end of the author list.Or, the custom template that is in the YAML header and that has the "author" line deleted may be used as well. An explanation in detail is provided at:
#https://github.com/rstudio/bookdown/issues/1158
remove_author <- function(x) {
  # identify empty author line
  i <- grep("^\\\\author\\{\\}$", x)
  # be sure it is the one pandoc inserts
  if(length(i) != 0 && grepl('^\\\\date\\{', x[i+1])) x <- x[-i]
  x
}
options(bookdown.post.latex = remove_author)
```

>>>>

library(patchwork)
library(tidyverse)
library(mvnfast)
library(nlme)
library(ggsci)
library(mgcv)
library(gratia)
library(ghibli)
library(viridis)
set.seed(1) #set seed for reproducibility

@@

#global themes for plotting
thm<-scale_color_viridis_d(option="magma",begin=0.1,end=0.7)
thm1<-scale_fill_viridis_d(option="magma",begin=0.1,end=0.7)#global theme for plotting

#thm<-scale_color_ghibli_d("MarnieMedium2",direction=-1) #global theme for plotting
#thm1<-scale_fill_ghibli_d("MarnieMedium2",direction=-1) #global theme for plotting

#this function will remove the default "author information" that is the Pandoc LaTeX template. Otherwise, and additional "and" will appear at the end of the author list.Or, the custom template that is in the YAML header and that has the "author" line deleted may be used as well. An explanation in detail is provided at:
#https://github.com/rstudio/bookdown/issues/1158
remove_author <- function(x) {
  # identify empty author line
  i <- grep("^\\\\author\\{\\}$", x)
  # be sure it is the one pandoc inserts
  if(length(i) != 0 && grepl('^\\\\date\\{', x[i+1])) x <- x[-i]
  x
}
options(bookdown.post.latex = remove_author)
```
